---
title: "NYPD Shooting Incident Data Report"
author: "Venkata Kasireddy"
date: "9/13/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
```


## R Markdown

#install tidyverse Package -- library(tidyverse)
```{r}
library(tidyverse)
```

#Read the data from DATA.Gov, NYPD Shooting Incident Data Report into uid_ny object
```{r}
uid_ny <- read_csv("https://data.cityofnewyork.us/api/views/5ucz-vwe8/rows.csv?accessType=DOWNLOAD")
```
#removing some columns from data that is not needed for the analysis
```{r}
uid_ny <- uid_ny %>% select (-c(OCCUR_TIME,PRECINCT,JURISDICTION_CODE,LOCATION_DESC,STATISTICAL_MURDER_FLAG,X_COORD_CD,Y_COORD_CD,Latitude,Longitude,`New Georeferenced Column` ))
```
#filtering rows where data is not avialable
```{r}
uid_ny <- uid_ny %>%  filter_at(vars(starts_with("PERP_")), any_vars(! is.na(.)))
```
#library(lubridate) -- to convert data char column to date object use the lubridate function
```{r}
library(lubridate)
```
#conevrt OCCUR_DATE (char) to occur_data (date object)

```{r}
uid_ny <- uid_ny %>% mutate( occur_date = mdy( OCCUR_DATE ) )

```
#remove chr OCCUR_DATE from uid_ny object

```{r}
uid_ny <- uid_ny %>% select (-c(OCCUR_DATE))
```
# Analysis -1 

#daily cases
```{r}
daily_cases <- uid_ny %>% count(occur_date)
```

#linear model (prediction/estimation number of cases per day based on history)
```{r}
mod1 <- lm(n ~ occur_date,data = daily_cases)
```
#dispaly statstical details of model
```{r}
summary(mod1)
```
#add new coloumn of est (estimate/prediction)
```{r}
daily_cases %>% mutate(est = predict(mod1))
```

#plot x axis as 'time', y axis number of shooting incidents, blue color as history, red color as estimate of linear #model   
```{r}
daily_cases %>% ggplot() + geom_point(aes(x = occur_date, y = n),color = "blue") + geom_point(aes(x = occur_date, y = predict(mod1)),color = "red") + labs(x = "Date",y = "shooting incidents",title = "NYPD shooting incidents",)
```

#Complete code to run above plot --- 
#daily_cases %>% ggplot() + geom_point(aes(x = occur_date, y = n),color = "blue") + geom_point(aes(x = occur_date, y = predict(mod1)),color = "red") + labs(x = "Date",y = "shooting incidents",title = "NYPD shooting incidents",)





# Analysis - 2 
#count by location (area wise with in new york)
```{r}
Location_count <- uid_ny %>% count(BORO)

Location_count
```


#Based on above data, Bronx and Brooklyn have highest number of incidents hence top two unsafe places where as #Staten Island is lowest cases hence safe place.













